Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-10-22 doc/Paper/main.tex
author fix

\author[a,1]{Andrina Nicola,}
\author[b]{David Alonso,}
\author[c]{An\v{z}e Slosar,}
\author[d,e]{Javier S\'anchez,}
\author[f]{Humna Awan,}
\author[f]{Adam Broussard,}
\author[b]{Zahra Gomes,}
\author[f]{Eric Gawiser,}
\author[x]{Rachel Mandelbaum,}
\author[g,h,i,j]{Hironao Miyatake,}
\author[k]{Jeffrey A. Newman,}
\author[x]{Ignacio Sevilla,}
\author[c,l]{Sarah Skinner,}
\author[x]{Erica Wagoner}

\affiliation[a]{Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton NJ 08544-0010, USA}
\affiliation[b]{Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, United Kingdom}
\affiliation[c]{Brookhaven National Laboratory, Physics Department, Upton, NY 11973, USA}
\affiliation[d]{Fermi National Accelerator Laboratory, Batavia, IL, 60510, USA}
\affiliation[e]{Department of Physics and Astronomy, University of California, Irvine, CA 92697, USA}
\affiliation[f]{Rutgers University, Physics \& Astronomy Department, Piscataway, NJ 08854, USA}
\affiliation[g]{Institute for Advanced Research, Nagoya University, Nagoya 464-8601, Japan}
\affiliation[h]{Division of Physics and Astrophysical Science, Graduate School of Science, Nagoya University, Nagoya 464-8602, Japan}
\affiliation[i]{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), UTIAS, The University of Tokyo, Chiba 277- 8583, Japan}
\affiliation[j]{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
\affiliation[k]{Department of Physics and Astronomy and PITT PACC, University of Pittsburgh, Pittsburgh, PA, 15260, USA}
\affiliation[l]{Department of Physics, Missouri University of Science and Technology, Rolla, MO 65401, USA}

>>>>

\author[a,1]{Andrina Nicola,}
\author[b]{David Alonso,}
\author[c,d]{Javier S\'anchez,}

\author[e]{An\v{z}e Slosar,}

\author[f]{Humna Awan,}
\author[f]{Adam Broussard,}
\author[b]{Zahra Gomes,}
\author[f]{Eric Gawiser,}
\author[x]{Rachel Mandelbaum,}
\author[g,h,i,j]{Hironao Miyatake,}
\author[k]{Jeffrey A. Newman,}
\author[x]{Ignacio Sevilla,}
\author[e,l]{Sarah Skinner,}
\author[x]{Erica Wagoner}

\affiliation[a]{Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton NJ 08544-0010, USA}
\affiliation[b]{Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, United Kingdom}
\affiliation[c]{Fermi National Accelerator Laboratory, Batavia, IL, 60510, USA}
\affiliation[d]{Department of Physics and Astronomy, University of California, Irvine, CA 92697, USA}
\affiliation[e]{Brookhaven National Laboratory, Physics Department, Upton, NY 11973, USA}
\affiliation[f]{Rutgers University, Physics \& Astronomy Department, Piscataway, NJ 08854, USA}
\affiliation[g]{Institute for Advanced Research, Nagoya University, Nagoya 464-8601, Japan}
\affiliation[h]{Division of Physics and Astrophysical Science, Graduate School of Science, Nagoya University, Nagoya 464-8602, Japan}
\affiliation[i]{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), UTIAS, The University of Tokyo, Chiba 277- 8583, Japan}
\affiliation[j]{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
\affiliation[k]{Department of Physics and Astronomy and PITT PACC, University of Pittsburgh, Pittsburgh, PA, 15260, USA}
\affiliation[l]{Department of Physics, Missouri University of Science and Technology, Rolla, MO 65401, USA}
